Finalized Plots

### 2022-10-17 Fish Data Analysis/Final_Plots.Rmd
Added new plots and added code for analysis

```{r}
library(tidyverse) #For dplyr and data sorting
library(ggplot2) #For plotting
library(bbmle) #For ICtab
library(car) #For Anova
library(forcats) #For Factor Work
library(ggpubr) #For the significance bars
```

@@

ggsave("Final Graphs/School_NND.png")
```

@@

ggsave("Final Graphs/Mean_Group_Size.png")
```

@@

ggsave("Final Graphs/Polarization.png")
```

@@

fish_speed_division <- speed_whole_school %>% inner_join(indiv_data_4_speed, by = c("Year", "Month", "Day", "Trial", "Tailbeat_Num")) %>%
                                              mutate(Divided_Speed = School_Speed/Mean_Speed)
```

@@

ggplot(fish_speed_division, aes(x = interaction(Ablation,Darkness,sep=", "), y = Divided_Speed, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on School Speed") +
  xlab("") +
  ylab("Speed (BL/s)") +
  ylim(0,8) +
  theme_light() +
  facet_wrap(~ Flow, strip.position = "bottom")+
  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
  stat_compare_means(comparisons = my_comparisons, label.y = c(6.5,7.5), label = "p.signif", hide.ns = TRUE) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

@@

@@

mi_fr_fl_a <- glm(turn_bool ~ Fish_Num_Ratio*Flow*Ablation, data = turning_data, family = binomial)

ggplot(turning_data, aes(x = Fish_Num_Ratio, y = turn_bool, color = Ablation))+
  geom_jitter(alpha = 0.1, height = 0.025)+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(mi_fr_fl_a, type="response"), color = Ablation, shape = Flow)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(mi_fr_fl_a, type="response"), color = Ablation, shape = Flow)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color,light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

@@

@@

>>>>

```{r}
library(tidyverse) #For dplyr and data sorting
library(ggplot2) #For plotting
library(bbmle) #For ICtab
library(car) #For Anova
library(forcats) #For Factor Work
library(ggpubr) #For the significance bars
library(report) #For the reports
library(emmeans) #For reporting
```

@@

ggsave("Final Graphs/School_NND.png")

nnd_glm <- glm(NND ~ 0 + Ablation + Darkness + Flow, data = school_data)s
Anova(nnd_glm)

#report(nnd_glm)

emmeans(nnd_glm, specs = pairwise ~ Ablation:Darkness:Flow)
emmeans(nnd_glm, specs = pairwise ~ Flow)
```

@@

ggsave("Final Graphs/Mean_Group_Size.png")

@@

ggsave("Final Graphs/Polarization.png")

polar_glm <- glm(School_Polar ~ 0 + Ablation + Darkness + Flow, data = school_data)
Anova(polar_glm)

emmeans(polar_glm, specs = pairwise ~ Ablation:Darkness:Flow)
emmeans(polar_glm, specs = pairwise ~ Flow)
```

@@

fish_speed_division <- speed_whole_school %>% inner_join(indiv_data_4_speed, by = c("Year", "Month", "Day", "Trial", "Tailbeat_Num")) %>%
                                              mutate(Divided_Speed = School_Speed/Mean_Speed,
                                                     Sub_Speed = ifelse(Flow == "Flowing Water (2 BL/s)", School_Speed - 2, School_Speed))
```

@@

ggplot(fish_speed_division, aes(x = interaction(Ablation,Darkness,sep=", "), y = Sub_Speed, fill = interaction(Ablation,Darkness,sep=", ")))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on School Speed") +
  xlab("") +
  ylab("Speed (BL/s)") +
  ylim(0,8) +
  theme_light() +
  facet_wrap(~ Flow, strip.position = "bottom")+
  #stat_compare_means(aes(label = ..p.signif..), method = "t.test", ref.group = "Flow 0, No Ablation, Light")
  stat_compare_means(comparisons = my_comparisons, label.y = c(6.5,7.5), label = "p.signif", hide.ns = TRUE) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

@@

speed_glm <- glm(Divided_Speed ~ 0 + Ablation + Darkness + Flow, data = fish_speed_division)
Anova(speed_glm)

emmeans(speed_glm, specs = pairwise ~ Ablation*Darkness*Flow - Ablation:Darkness)
emmeans(speed_glm, specs = pairwise ~ Flow)

@@

#mi_fr_fl_a <- glm(turn_bool ~ Fish_Num_Ratio*Flow*Ablation, data = turning_data, family = binomial)

mi_fr_fl <- glm(turn_bool ~ Fish_Num_Ratio*Flow, data = turning_data, family = binomial)

ggplot(turning_data, aes(x = Fish_Num_Ratio, y = turn_bool, color = Flow))+
  geom_jitter(alpha = 0.1, height = 0.025)+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(mi_fr_fl, type="response"), color = Flow)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(mi_fr_fl, type="response"), color = Flow)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

@@

turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*(Flow+Darkness+Ablation), data = turning_data, family = binomial)
Anova(turning_glm)

report(turning_glm)
emmeans(turning_glm, specs = pairwise ~ Flow)

@@

```
#Demo graph for startle experiments
```{r}

startle_data <- tibble(Darkness = rep(c("Light","Dark"), each = 100),
                       Trial = rep(rep(c("1","10","20","30"), each = 25), 2),
                       NND = c(rnorm(100,1,0.1),
                               rnorm(25,1.5,0.25),rnorm(25,1.33,0.2),rnorm(25,1.16,0.15),rnorm(25,1,0.1)))

ggplot(startle_data, aes(x = Trial, y = NND, fill = Darkness))+
  geom_boxplot(outlier.shape = NA) +
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Startle Trial Number (NND)") +
  xlab("Startles #") +
  ylab("NND (BL)") +
  theme_light()
